---
title: "Programming Background"
author: "Xin Wang"
date: '2022-06-07'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="../images/")
```

```{r, eval=FALSE}
rmarkdown::render(
    '/Users/ceciliawang/Desktop/ST558/git/xinceciliaw.github.io/_Rmd/2022-06-07-second-blog-post.Rmd', 
    output_format = "github_document",
    output_dir = "/Users/ceciliawang/Desktop/ST558/git/xinceciliaw.github.io/_posts",
    output_options = list(
      html_preview = FALSE
    )
)
```

rmarkdown::render(
    '2022-06-03-programming-background.Rmd', 
    output_format = "github_document",
    output_dir = "../_posts",
    output_options = list(
      html_preview = FALSE
    )
)

/Users/ceciliawang/Desktop/ST558/git/xinceciliaw.github.io/_Rmd
/Users/ceciliawang/Desktop/ST558/git/xinceciliaw.github.io/_Rmd/

## Prompt One
aa
Everyone in this course had some programming experience coming in (due to the prerequisites).  What are your thoughts on R vs whatever other software you've used?  What functionality do you like about R?  What parts do you miss about your other language?  Do you consider R a difficult language to learn? (If you knew R prior to the course, describe your experience when first learning it.)

## Example R Markdown output

```{r}
plot(iris)
```

